---
title: "Analysis of mtcars dataset"
author: "hyeonsu Noh"
date: '2022-08-17'
output:
  slidy_presentation: default
  ioslides_presentation: default
---

### mtcars dataset
- Description :
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

- Source :
Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.


### Data format - mtcars
A data frame with 32 observations on 11 (numeric) variables.

| Index | Field |Detail |
------- | ----- | ------ |
| [, 1]	| mpg	| Miles/(US) gallon |
| [, 2]	| cyl	| Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp |	Gross horsepower |
| [, 5]	| drat |	Rear axle ratio |
| [, 6]	| wt |	Weight (1000 lbs) |
| [, 7]	| qsec |	1/4 mile time |
| [, 8]	| vs |	Engine (0 = V-shaped, 1 = straight) |
| [, 9]	| am |	Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear |	Number of forward gears |
| [,11]	| carb |	Number of carburetors |


### UI Code
```{r, eval = FALSE, echo = TRUE}
library(shiny)

shinyUI(
  navbarPage("Shiny Application",
             tabPanel("Analysis",
                      fluidPage(
                        titlePanel("The relationship between variables and miles per gallon (MPG)"),
                        sidebarLayout(
                          sidebarPanel(
                            selectInput("variable", "Variable:",
                                        c("Number of cylinders" = "cyl",
                                          "Displacement (cu.in.)" = "disp",
                                          "Gross horsepower" = "hp",
                                          "Rear axle ratio" = "drat",
                                          "Weight (lb/1000)" = "wt",
                                          "1/4 mile time" = "qsec",
                                          "V/S" = "vs",
                                          "Transmission" = "am",
                                          "Number of forward gears" = "gear",
                                          "Number of carburetors" = "carb"
                                        )),
                            
                            checkboxInput("outliers", "Show BoxPlot's outliers", FALSE)
                          ),
                          
                          mainPanel(
                            h3(textOutput("caption")),
                            
                            tabsetPanel(type = "tabs", 
                                        tabPanel("BoxPlot", plotOutput("mpgBoxPlot")),
                                        tabPanel("Regression model", 
                                                 plotOutput("mpgPlot"),
                                                 verbatimTextOutput("fit")
                                        )
                            )
                          )
                        )
                      )
             ),
            
             tabPanel("More Data Detail",
                      h2("Motor Trend Car Road Tests"),
                      hr(),
                      h3("Description"),
                      helpText("The data was extracted from the 1974 Motor Trend US magazine,",
                               " and comprises fuel consumption and 10 aspects of automobile design and performance",
                               " for 32 automobiles (1973-74 models)."),
                      h3("Format"),
                      p("A data frame with 32 observations on 11 variables."),
                      
                      p("  [, 1]   mpg         Miles/(US) gallon"),
                      p("  [, 2]	 cyl	 Number of cylinders"),
                      p("  [, 3]	 disp	 Displacement (cu.in.)"),
                      p("  [, 4]	 hp	 Gross horsepower"),
                      p("  [, 5]	 drat	 Rear axle ratio"),
                      p("  [, 6]	 wt	 Weight (lb/1000)"),
                      p("  [, 7]	 qsec	 1/4 mile time"),
                      p("  [, 8]	 vs	 V/S"),
                      p("  [, 9]	 am	 Transmission (0 = automatic, 1 = manual)"),
                      p("  [,10]	 gear	 Number of forward gears"),
                      p("  [,11]	 carb	 Number of carburetors"),
                      
                      h3("Source"),
                      
                      p("Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.")
             ),
           
  )
)
```

### Server Code
```{r, eval=FALSE, echo = TRUE}
library(shiny)
library(datasets)

mtcars
mtcars$am <- factor(mtcars$am, labels = c("Automatic", "Manual"))

shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("mpg ~", input$variable)
  })
  
  formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")
  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mtcars)
  })
  
  output$caption <- renderText({
    formulaText()
  })
  
  output$mpgBoxPlot <- renderPlot({
    boxplot(as.formula(formulaText()), 
            data = mtcars,
            outline = input$outliers)
  })
  
  output$fit <- renderPrint({
    summary(fit())
  })
  
  output$mpgPlot <- renderPlot({
    with(mtcars, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })
  })
  
})

```

```{r}

```

